---
title: "Bayesian Ranking"
subtitle: "Interpreting Product Reviews"
author: "Tobias Heidler"
date: "21/11/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
library(kableExtra)
library(scales)

theme_set(
  theme_dark() +
    theme(legend.position = "bottom")
)
```

## Introduction

- Product Reviews are hard to interpret
- There is no easy way to know if you should choose between a 4,7 stars review with one hundreds reviews or one with five 5-star reviews
- And no one considers **you** - the expert - in the rankings

But now we have a solution: **The Bayesian Ranking Tool**

## Technology

- This Tool uses top of the line Bayesian algorithms to help you through your purchasing process
- Just type in all the votes &
- Choose how good the product is in **your** view * & 
- How confident **you** are with your point of view * &
- How much risk **you** are willing to take

 * Optional!

## Example

```{r}
tribble(~Name, ~`5 Stars`, ~`4 Stars`, ~`3 Stars`,~`2 Stars`, ~`1 Stars`,
        "Product 1", 190, 15, 10, 2, 5,
        "Product 2", 5, 0, 0, 0, 0) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))
```

**You** consider Product 2 to be slightly better than Product 1. **You** are relatively confident. **You** want to be 90% sure!

## Result

```{r}
x <- seq(.1,1,.01)
df1 <- tibble(Stars = x,
              Name = "Product 1") %>% 
        mutate(`P(Stars | Votes)` = dbeta(x,
                                          .8 * 222 + 190 + 15 * 3/4 + 10 * 2/4 + 2 * 1/4 + 5 * 0 + 1, 
                                          .2*222 + 190 * 0 + 15 * 1/4 + 10 * 2/4 + 2 * 3/4 + 5 * 1 + 1),
               `P(Stars | Votes)` = `P(Stars | Votes)` / sum(`P(Stars | Votes)`))

df2 <- tibble(Stars = x,
              Name = "Product 2") %>% 
        mutate(`P(Stars | Votes)` = dbeta(x,
                                          .9 * 5 + 6, 
                                          .1 * 5 + 1),
               `P(Stars | Votes)` = `P(Stars | Votes)` / sum(`P(Stars | Votes)`))

Posterior.Confidence <- tribble(~Name, ~Limit,
                                "Product 1", qbeta(.1,
                                                    .8 * 222 + 190 + 15 * 3/4 + 10 * 2/4 + 2 * 1/4 + 5 * 0, 
                                                    .2*222 + 190 * 0 + 15 * 1/4 + 10 * 2/4 + 2 * 3/4 + 5 * 1)* 4 + 1,
                                "Product 2", qbeta(.1,
                                                    .9 * 5 + 5, 
                                                    .1 * 5) * 4 + 1)
Posterior.Data <- df1 %>% 
                    bind_rows(df2) %>% 
                    mutate(Stars = Stars * 4 + 1)

ggplot(Posterior.Data,
                 aes(x = Stars,
                     y = `P(Stars | Votes)`,
                     color=Name)) +
              geom_vline(data=Posterior.Confidence,
                         aes(xintercept=Limit, color=Name),
                         linetype="dashed") +
              geom_line() +
              scale_color_brewer(type="qual", palette = "Set2") +
              scale_y_continuous(labels = label_percent()) +
              coord_cartesian(xlim = c(1,5))
```

**You** should take Product 2! Bayesian magic at it's best!

## Summary

- The tool can help you with every purchase
- It is highly customizable and blends **your** expert knowledge and crowd knowledge seamlessly
- Try it yourself: [Link](https://pteridin.shinyapps.io/RBayesianRanking/)

Happy purchase!